% =============================================================================
% FILE: /sections/03_theory.tex
% PURPOSE: To explain our theoretical model and results.
% Written by the Theoretical Modeling team.
% NOTE: The formal math (definitions, theorems) is in /model/math_framework.tex.
% This file IMPORTS that math and provides the intuitive, plain-English
% explanations that make it understandable.
% =============================================================================
\section{Theoretical Framework}\label{sec:theory}

% --- IMPORT THE FORMAL MODEL SETUP ---
% This command inserts the content from the math_framework.tex file.
\input{model/math_framework.tex}

% Now, provide the intuitive walkthrough for the model that was just imported.

\subsection{Intuition Behind the Model}
The model presented in Section \ref{sec:model} formalizes the simple idea of the "lunch menu" problem discussed in the introduction. We define individuals by their observable traits ($Z_i, g_i$), their hidden menu of options ($C_i$), and their preferences ($u_i(\cdot)$). The key element is that the researcher cannot see $C_i$. This single assumption—that choice sets are latent—is the engine that drives all of our results. By assuming that the availability of these choice sets can depend on an individual's group (Assumption 1), we build a world where access to opportunity can be systematically unequal.

\subsection{Explaining the Main Results}
Our model generates three main theoretical results, which we state formally as Theorems \ref{thm:non_id} through \ref{thm:networks}. Here, we explain the intuition behind each.

\subsubsection{Why the Treatment Effect is Not Identified (Theorem \ref{thm:non_id})}
Theorem \ref{thm:non_id} is a negative but crucial result. It states that if we do not know who could have accessed a program, we can never know for sure if the program worked. The proof provides a stark example: imagine two groups of people who all enrolled in a tutoring program. In one world, they all had other options but chose tutoring because it was the most effective. In another world, they had no other options and were forced into it. The observed data on enrollment and outcomes could look identical in both worlds, but the true effectiveness of the program would be completely different. Because we cannot distinguish between these worlds from the data alone, the effect is not "point identified."

\subsubsection{What We Can Still Learn: Partial Identification (Theorem \ref{thm:bounds})}
While we cannot pin down a single number for the treatment effect, we are not left with nothing. Theorem \ref{thm:bounds} shows that we can derive a "range of possibilities" for the true effect. The logic is to ask: "Given what we observe, what is the most optimistic and most pessimistic scenario consistent with the data?" For example, the pessimistic scenario might assume that all the high-performing individuals who took the treatment would have done just as well without it. The optimistic scenario might assume the opposite. The true effect must lie somewhere between these two extremes. The width of this range, or the "bounds," becomes a measure of our fundamental uncertainty.

\subsubsection{How Social Networks Make Things Worse (Theorem \ref{thm:networks})}
Theorem \ref{thm:networks} connects our model to the real world of referrals and social connections. It makes two points. First, when opportunities spread through segregated social networks ("homophily"), it destroys the useful variation a researcher needs. Instead of having some treated and some untreated people within the same group to compare, you might have one group where everyone has access and another where no one does. This makes it almost impossible to separate the effect of the treatment from the underlying differences between the groups. Second, this is inefficient. An opportunity for a talented student might never reach them simply because it gets "stuck" in a different social circle, leading to a loss for both the student and society.